Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-05-07 main.Rmd
removed mention of altering-tick operation from paper

\newtheorem{definition}{Definition}[section]

@@

\begin{example}
{\rm Consider a linear granularity $G'$ such that $G' = Alter^{2}_{(1,-2)}(B, Group_7(B))$, which implies it is made up of shrinking every 1st granule of $Group_7(B)$ by $2$ granules. Then $Q_{B, G'}$ is a repetitive categorization of time, similar to circular granularities, except that the number of granules of $B$ is not necessarily the same across different granules of $G'$. Here, $T_0 = \{0, 1, 2, 3, 4, 5, 6\}$ and $T_1 = \{7, 8, 9, 10, 11\}$. Hence using Definition \autoref{def:quasicircular} we will have:

@@

>>>>

\newtheorem{definition}{Definition}

@@

\begin{example}
{\rm Consider $G'$ such that every two consecutive granules of $G'$ are made up of $7$ and $5$ granules of $B$ respectively within each period of the grouping ($B$, $G'$). Then $Q_{B, G'}$ is a repetitive categorization of time, similar to circular granularities, except that the number of granules of $B$ is not necessarily the same across different granules of $G'$. Here, $T_0 = \{0, 1, 2, 3, 4, 5, 6\}$ and $T_1 = \{7, 8, 9, 10, 11\}$. Hence using Definition \autoref{def:quasicircular} we will have:

@@

<!--such that $G' = Alter^{2}_{(1,-2)}(B, Group_7(B))$, which implies it is made up of shrinking every 1st granule of $Group_7(B)$ by $2$ granules.-->
